Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-08-31 manuscript_thev_transcriptome.Rmd
Reduce figure resolutions and fix mardown pdf

---
title: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus
always_allow_html: true
output:
  # word_document: default
  html_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
bibliography: transcriptome_refs.bib
csl: asm.csl
editor_options:
  chunck_output_type: console
---
\vspace{5mm}

@@

```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(tibble)
library(scales)
library(gt)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

@@

```{r}
gt(tab1) %>%
  fmt_markdown()
```

@@

```{r}
gt(sig_12_juncs)
```

@@

```{r}
gt(sig_24_juncs)
```

@@

```{r}
gt(sig_72_juncs)
```

>>>>

---
title: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus
output:
  word_document: default
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
bibliography: transcriptome_refs.bib
csl: asm.csl
editor_options:
  chunck_output_type: console
---
\vspace{5mm}

@@

```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(tibble)
library(scales)
library(kableExtra)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

@@

```{r}
tab1 %>%
kbl(format = "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
  row_spec(0, font_size = 15) %>%
  column_spec(1, bold = T)

```

@@

```{r}
sig_12_juncs%>%
  kbl(format = "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
  row_spec(0, font_size = 15)
```

@@

```{r}
sig_24_juncs %>%
  kbl(format = "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
  row_spec(0, font_size = 15)
```

@@

```{r}
sig_72_juncs %>%
  kbl(format = "latex") %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
  row_spec(0, font_size = 15)
```
